Stat 400 Project

### 2021-12-04 Stat 400 proj.Rmd
bugs

  #generated days of recovery times for each person
  recovery_days <- rpois(num_subjects,14)

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  return(df)
}

@@

#Function for getting updated coordinates
update_coords <- function(og_df, delta_df){
  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=3)
  new_df <- data.frame(new_mx)
  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
  new_df[,3] <- og_df[,3]
  colnames(new_df) <- c('x', 'y', 'subjects')

  new_df
}

@@

  current_recovered <- state[state[,3]=='Rec',]

@@

@@

      z_s <- as.numeric(current_recovered[i,'Rec'])

@@

      if(d <= crucial_distance){
        new_status[j] <- 'I'
        newly_infected <- c(newly_infected, j)
      }
      #check recovery time for person at z_s
      if(z_s>=t){
        new_status[j] <- 'Rec'
      }
      else{
        new_status[j] <- 'S'
      }
    }
  }

@@

get_recovery_time <- function(){

}

@@

  recovery_time <- c()

@@

      r_times <-

>>>>

  #pregenerated days of recovery times for each person
  recovery_days <- rpois(num_subjects,14)
  inc_time <- rpois(num_subjects,5)

  #Put into a data frame
  df <- as.data.frame(cbind(as.numeric(start_x), as.numeric(start_y), subjects,recovery_days,inc_time))
  colnames(df)[1] <- 'x'
  colnames(df)[2] <- 'y'
  colnames(df)[3] <- 'subjects'
  colnames(df)[4] <- 'recovery'
  colnames(df)[5] <- 'incubation'
  return(df)
}

@@

#Function for getting updated coordinates
update_coords <- function(og_df, delta_df){
  new_mx <- matrix(data=NA, nrow=nrow(og_df), ncol=5)
  new_df <- data.frame(new_mx)
  new_df[,1] <- as.numeric(og_df[,'x']) + delta_df[,'delta_x']
  new_df[,2] <- as.numeric(og_df[,'y']) + delta_df[,'delta_y']
  new_df[,3] <- og_df[,3]
  new_df[,4] <- og_df[,4]
  new_df[,5] <- og_df[,5]
  colnames(new_df) <- c('x', 'y', 'subjects', 'recovery', 'incubation')
  new_df
}

@@

@@

  #is this right do get the list of recovery days?
  current_rec_time <- state[state[,4]]

@@

      z_s <- as.numeric(current_rec_time[i])

@@

      if(d <= crucial_distance){
        new_status[j] <- 'I'
        newly_infected <- c(newly_infected, j)
      }

      #check recovery time for person at z_s. If their recovery day time is past the current day, they recovered. 
      if(z_s>=t){
        new_status[j] <- 'Rec'
      }

      else{
        new_status[j] <- 'S'
      }
    }
  }

@@

@@

  recovery_time <- initial_data[,4]

@@
